Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-07 prob.tex
prob.tex \section{Proofs} Specify the current problem...

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole, then $\theta\left(\ket{\psi}\right)$ denotes the the
latitude of $\ket{\psi}$.\qed\end{definition}

@@

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on the latitude~$\theta$
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\min_{n\ge\max\left\{ 2\pi,\frac{\pi^{2}}{\theta}\right\} }2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$\footnote{\yutsung{Notice that \cite{RichmanBridges1999} derives the modulus
of continuity~$\omega_{f}\left(\delta\right)$ in their Corollary~18(?).
Maybe need to upgrade and derive the modulus of continuity in our
case later.}}. Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with $\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
Let $a$ be the difference in longitudes of $\ket{\psi}$ and $\ket{\psi'}$.
Take $n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$ steps along
east-west great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
to a point $\ket{\psi_{s}}$, and the details in the original proof...}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
typed...}},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
then 
\begin{itemize}
\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
latitude of $\ket{\psi}$.
\item $N_{\ket{0}}$ denotes the northern hemisphere.
\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
a plane containing the center of $S^{2}$.
\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
great circle tangent to the circle of latitude through $\ket{\psi}$;
we shall call it East-West great circle through $\ket{\psi}$, and
denoted by $C\left(\ket{\psi}\right)$.
\end{itemize}
\qed\end{definition}

\begin{conjecture}\cite{Hamhalter2013}~Let $\ket{\psi}$ and $\ket{\psi'}$
be points in $N_{\ket{0}}$ with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
Then there exist a finite number~$n$ steps along east-west great
circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due
south of $\ket{\psi}$.

The problem is whether number~$n$ could be picked uniformly? Or
there is a number~$n$ satisfying the given conditions for all latitude?

Notice that the proof in \cite{RichmanBridges1999} doesn't require
the number~$n$ to be picked uniformly because we could always pick
$f\left(p\right)=0$ in Lemma~20 in \cite{RichmanBridges1999}. However,
in the corresponding lemma~\ref{lemma:analogLemma20RichmanBridges1999},
we need to deal with the case where $\eta$ doesn't approach $0$
because the maximum and minimum value may not be orthogonal in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.\qed\end{conjecture}

@@

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on the latitude~$\theta$
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\min_{n\ge\max\left\{ 2\pi,\frac{\pi^{2}}{\theta}\right\} }2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$\footnote{\yutsung{Notice that \cite{RichmanBridges1999} derives the modulus
of continuity~$\omega_{f}\left(\delta\right)$ in their Corollary~18(?).
Maybe need to upgrade and derive the modulus of continuity in our
case later.}}. Let $\ket{\psi}$ and $\ket{\psi'}$ be points in $N_{\ket{0}}$
with $\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
Let $a$ be the difference in longitudes of $\ket{\psi}$ and $\ket{\psi'}$.
Take $n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$ steps along
East-West great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
to a point $\ket{\psi_{s}}$, and the details in the original proof...}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
typed...}},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.
